%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Stylish Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Stefano (http://stefano.italians.nl/archives/63)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% The two fonts used in this template: Adobe Garamond Pro and Gill Sans
% do not come with Windows by default. You will need to download them in
% order to get an output as in the preview PDF. Otherwise, change those 
% fonts to fonts that do come with Windows or comment out the lines to use 
% the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% ------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
% ------------------------------------------------------------------------------

\documentclass{scrlttr2}

\usepackage{fontspec} % system fonts
% \usepackage{marvosym} % use symbols

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage[osf,sc]{mathpazo}
\usepackage{hyperref}

\usepackage{letterspace}  % for "\lsstyle" macro
\usepackage{xcolor}

% Removes all indentation from paragraphs
\setlength\parindent{0pt}

% Sets the font size and leading
% \renewcommand{\normalsize}{\fontsize{12.5}{17}\selectfont}

%-------------------------------------------------------------------------------
% PERSONAL INFORMATION
%-------------------------------------------------------------------------------

% Your name
\setkomavar{fromname}{MATHEUS V. CORREA}

% Your address
\setkomavar{fromaddress}{Rua Catharina S. Vicentin, 34\\Campinas, Brazil}

% Your phone number
\setkomavar{fromphone}{+55~(43)~99615~3091} 

% Your email address
\setkomavar{fromemail}{matheusviniciuscorrea@gmail.com}

% Date format
% \setkomavar{date}{14 January 2022}

% City written before the date
\setkomavar{place}{Campinas, Brazil}

% Your name as you want it to appear in the signature
\setkomavar{signature}{Matheus Correa.}

% ------------------------------------------------------------------------------

\KOMAoptions{
  % paper=letter,
  fontsize=11pt,
  parskip=half,
  backaddress=off,
  fromalign=right,
  fromphone=on,
  foldmarks=false,
  fromemail=true,
  % addrfield=off,
  fromrule=aftername,
}

\newcommand{\spacedsc}{\scshape\Large}

\setkomafont{fromname}{\spacedsc}
\setkomafont{backaddress}{\mdseries}
\setkomafont{pagenumber}{\sffamily}
\setkomafont{subject}{\bfseries}

\makeatletter
\@setplength{firstheadvpos}{10mm}%
\@setplength{refvpos}{80mm}%
\makeatother

% \firsthead{%
%   \centering%
%   {\addfontfeature{LetterSpace=20.0}\scshape \LARGE \usekomavar{fromname}}
% }

\firstfoot{%
  \centering\footnotesize%
  {Matheus Correa} \ $\cdot$ \ \usekomavar{fromemail} \ $\cdot$ \
  \href{}{www.linkedin/in/matheusvcorrea}%
}

%-------------------------------------------------------------------------------

\begin{document}

\renewcommand{\enclname}{Enclosures}

\begin{letter}{% Addressed to the company you are applying to
    % Mrs. Jane Smith\\
    % Recruitment Officer\\
    Talkdesk, Inc.\\
    545 Mission Street, 12th floor\\
    San Francisco, CA 94105%
  }

  \opening{Dear Mrs./Ms. Recruiter,}

  I'm thrilled to apply for Software Engineer positions at Taskdesk, Inc. and
  share my work with people that have the same passion for technology as
  me. Furthermore I believe that my high education levels at prestigious
  institutions at Brazil and reach professional experience makes me fit for the
  role.

  I started with software development at 16 years-old where I start to tech
  myself web systems programming. This period before the university I offered my
  work as freelancer focusing on e-commerce. This then leads me to a bachelor's
  and master's degree in theory of computation. Today I hold a position in an
  strategic team inside an important insurance company.

  The key skills and experiences that I can put at service and believe may be
  taken advantage of by your the company are the following:

  \begin{itemize}
  \item Strong knowledge of software and machine learning engineering and its
    life cycle under microservices architecture.
  \item A 5+ years broad work experience that vary from e-commerce industry to
    risk scoring predictions at insurance industry gives me a mature look at
    what high quality solutions should looks like.
  \item Programming under C++, Python, Java, and among others stacks.
  \end{itemize}

  In addition to the above I mention my personal interest in ethical and high
  performance computer systems where I can apply all my highest academic and
  career background to accomplish the most demanding tasks. That said I would
  welcome the opportunity to discuss my application. I hope to hear from
  you. Thank you for your consideration.

  \closing{Sincerely,}

  \encl{R\'esum\'e.} % enc

\end{letter}
\end{document}

%%% Local Variables: 
%%% coding: utf-8
%%% mode: latex
%%% TeX-engine: xetex
%%% End: 
